---
title: "Primer Design"
---

```{r setup.1, include=FALSE}
knitr::opts_chunk$set(echo = TRUE, fig.path = "images/")
```

```{r setup.2}
library(ggplot2, warn.conflicts = FALSE)
```

# Reading in data

ARG counts by sample:

```{r read_data.1}
arg_counts <- read.delim("arg_counts.edit", sep = "\t", row.names = 1)
head(arg_counts)
```

ARG totals by factors:

```{r arg_totals.1}
arg_means <- read.delim("arg_means.tsv", sep = "\t", row.names = 1)
head(arg_means)
```


Positive (negative) value $x$ indicate there is $x$ more (less) of a gene detected in manure.

```{r manure_data.1}
manure.means <- arg_means[, c(1:3)]
head(manure.means)
```



Adding column for differential abundances between pig- and cow-associated manure
```{r manure_data.2}
manure.means$manure.pig_beef.diffs <- manure.means$manure.pig.mean - manure.means$manure.beef.mean
head(manure.means)
```

# Bootstrapping

```{r load_bootstrap_package.1}
library(boot)
```

Create a mean function for use with bootstrapping.

```{r bootstrapping.1}
boot.mean <- function(x, d) {
  return(mean(x[d]))
}
```

Bootstrapping of mean abundance for manure-pig samples.

```{r bootstrapping.2}
boot.manure.pig <- boot(manure.means$manure.pig.mean, boot.mean, R = 10000)
summary(boot.manure.pig)
```

```{r bootstrapping.3}
plot(boot.manure.pig, index = 1)
```

```{r bootstrapping.4}
boot.ci(boot.manure.pig, type = "bca")
```

Thus, according to our bootstrap, any genes with observed abundances higher than 155 in the `manure-pig` treatment should be considered significant.  The list of genes higher than that abundance in the `manure.pig` treatments are:

```{r bootstrapping.5}
(sig_genes.manure.pig <- row.names(manure.means[manure.means$manure.pig.mean > 155, ]))
```

We repeat this process for the `manure.beef` treatments.  We first create a function to automate this:
```{r bootstrapping.6}
get_sig_genes <- function(df, treat, r = 10000)
{
  bootstrap <- boot(df[, treat], boot.mean, R = r)
  bootstrap.results <- boot.ci(bootstrap, type = "bca")
  upper_cutoff <- bootstrap.results$bca[5]
  return(row.names(df[df[, treat] > upper_cutoff, ]))
}
```

Now we can feed it our data frame and treatment to `get_sig_genes` to get a list of significant genes for that ground-animal treatment.  Passing the data frame `manure.means` and the treatment `manure.beef`, our genes are:

```{r bootstrapping.7}
(sig_genes.manure.beef <- get_sig_genes(manure.means, "manure.beef.mean"))
```